\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}

\usepackage{lmodern}
\usepackage[T1]{fontenc}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.475in}
\addtolength{\evensidemargin}{-0.475in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.75in}
\addtolength{\textheight}{1.5in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2.5pt}}
  }
}


\newcommand{\resumeItemAIDS}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-6.5pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-3pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-6pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4.5pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}
\newcommand\tab[1][1cm]{\hspace*{#1}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{http://r333d.com/}{\Large Reed Weichler}} \href{mailto:rweichler@gmail.com}{rweichler@gmail.com} |
  \href{https://r333d.com}{r333d.com} |
  \href{https://github.com/rweichler}{github.com/rweichler} |
  \href{https://twitter.com/rweichler}{twitter.com/rweichler}
\end{tabular*}

%-----------WORK EXPERIENCE-----------------
\section{Experience}
 
  \resumeSubHeadingListStart
  
    \resumeSubheading
      {Superhuman}{San Francisco, California}
      {Software Engineer}{May 2018 - Aug 2019}
      \resumeItemListStart
        \item\small{
        Email productivity startup. Notable users: Steve Huffman (Reddit), Michael Lopp (Apple/Slack), Nat Friedman (Github).
        
        It was a small company when I joined. 6 engineers (including me) + 2 engineering managers. I worked with a team of 4 on the iOS app (Swift, Objective-C, C++, JavaScript). I also occasionally contributed to the web frontend (Electron / React) and the backend (Go / Postgres / Redis / GCP).
        
        On the iOS side I fixed many crashes/bugs that affected thousands of paying users, added UI/UX improvements to make navigating the app easier and more pleasant, automated the build system to tag the git repo for easier debugging, reduced a significant amount of tech debt, and more.}
      \resumeItemListEnd
  
    \resumeSubheading
      {Cydia}{}
      {Indie iOS Developer}{Feb 2014 - May 2018}
      \resumeItemListStart
        \item\small{See "Cydia Products" section for more details.
        }
      \resumeItemListEnd

    \resumeSubheading
      {Quixey}{Palo Alto, California}
      {Software Engineer (Intern)}{Jan 2012 -- July 2012}
      \resumeItemListStart
        \item\small{
        Helped build the Quixey Challenge (recruiting tool) using the Meteor framework (JavaScript).
        }
      \resumeItemListEnd

  \resumeSubHeadingListEnd


\section{Cydia Products}
  \resumeSubHeadingListStart
    \resumeSubItem{EQE (released 2017) / EqualizerEverywhere (released 2014)}{EQE has two components. A system-wide parametric equalizer (the only of its kind) and a  \href{https://last.fm}{Last.FM}-like service that lets users create a profile, track their playback history, post on a message board, and keep a backup of their presets online. The iOS side required reverse engineering, audio DSP, app development, and low-level iOS systems engineering. Server-side, I used OpenResty (an nginx distribution) for the application, with Postgres for persistent storage and Redis as a message broker. It can handle about 10K requests per second on a cheap \$3.50 VPS. It used to be a commercial product until Cydia Store shut down in December 2018. About 8,000 weekly active users. More info: \href{https://eqe.fm/about}{eqe.fm/about} }
    \resumeSubItem{Cylinder (released 2014)}{Animation "platform" that exposes a Lua API for cool icon animations when swiping on the home screen. Over 2.5 million total downloads and probably more than 100K active users. \\ Review: \href{https://youtube.com/watch?v=Y-Pk-XDVj-o}{youtube.com/watch?v=Y-Pk-XDVj-o}
    Source: \href{https://github.com/rweichler/cylinder}{github.com/rweichler/cylinder}
    
    }
  \resumeSubHeadingListEnd
  
%-----------PROJECTS-----------------
\section{Open Source Contributions}
  Non-exhaustive.\vspace{-2pt}
  \resumeSubHeadingListStart
    \resumeSubItem{Zebra}
      {Initial R\&D and localization support. \href{https://github.com/wstyres/zebra}{https://github.com/wstyres/zebra}}
    \resumeSubItem{Cylinder}
      {Author / Maintainer. \href{https://github.com/rweichler/cylinde}{https://github.com/rweichler/cylinder}}
    \resumeSubItem{gmusicapi}
      {Reduced network usage for certain types of tracks. \href{https://github.com/simon-weber/gmusicapi}{https://github.com/simon-weber/gmusicapi}}
      
  \resumeSubHeadingListEnd

%-----------PROJECTS-----------------
\section{Other Projects}
    Non-exhaustive.\vspace{-2pt}
  \resumeSubHeadingListStart
    \resumeSubItem{Meatpick}
      {Basic Calendly clone. \href{http://meatpick.com}{http://meatpick.com}}
    \resumeSubItem{gbrc}
      {Gameboy emulator, written from scratch in C. Runs Pokemon Red.}
    \resumeSubItem{Lucy}
      {Lua / Objective-C bridge and runtime analysis/debugging tool for iOS. \href{https://github.com/rweichler/lucy}{https://github.com/rweichler/lucy}}
    \resumeSubItem{jjjj}
      {GUI package manager for iOS (based on dpkg, similar to Cydia).  \href{https://github.com/rweichler/jjjj}{https://github.com/rweichler/jjjj}}
    \resumeSubItem{Aite}
      {Custom build system used to develop software for Cydia. \href{https://github.com/rweichler/aite}{https://github.com/rweichler/aite}}
    \resumeSubItem{Sunnyveil}
      {3D game engine written in C and LuaJIT. Has Lua bindings to Bullet (physics engine) and OpenGL.}
    \resumeSubItem{Wuigi}
      {Mario clone (kind of like Mario Maker), written in Java. \href{https://github.com/rweichler/wuigi}{https://github.com/rweichler/wuigi}}
    \resumeSubItem{Luna Roja}
      {Edit of mGBA, giving online multiplayer to Pok\'emon Red.  \href{https://hax.iimarckus.org/topic/7112/}{https://hax.iimarckus.org/topic/7112/}}
  \resumeSubHeadingListEnd

  
%-----------SKILLS-----------------
\section{Skills}
    \resumeItemListStart
        \resumeItemAIDS{Languages}
            {C/C++, Lua/LuaJIT, Objective-C, Swift, JavaScript, Python, Go}
        \resumeItemAIDS{Tools / Software}
            {SQLite, C FFIs, OpenGL, Git, Vim, devKitARM (Nintendo 3DS toolchain)}
        \resumeItemAIDS{Backend / Infra}
            {OpenResty (nginx "distribution"), Postgres, FreeBSD, Redis}
        \resumeItemAIDS{iOS}
            {Core Audio, Xcode, build automation, Objective-C / LuaJIT interop, Realm, IDA, cycript, MobileSubstrate, Objective-C runtime, inter-process communication, RxSwift}
    \resumeItemListEnd


%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubItem
      {Recurse Center}{Jan 2020 -- March 2020}
    \resumeSubItem
      {UC Davis}{Computer Science, Class of 2017}
    \resumeSubItem
      {Homestead High School}{Cupertino, California}
  \resumeSubHeadingListEnd


\end{document}

